A Monte Carlo Synthetic Acceleration Method for Solving the Thermal Radiation Diffusion Equation

### 2012-05-26 doc/jcomp2012/jcomp2012.tex
Adding images from nse07 paper

%%---------------------------------------------------------------------------%%
\begin{abstract}
%% Text of abstract

@@

%% main text
%%---------------------------------------------------------------------------%%
\section{}
\label{}

>>>>

  %%---------------------------------------------------------------------------%%
  \begin{abstract}

    We present a synthetic-acceleration based Monte Carlo method for
    solving the 1T thermal radiation diffusion equations.  We show
    that this method can be an effective solver for sparse matrix
    systems.  We also discuss its general applicability to broader
    classes of problems.

@@

%% main text
%%---------------------------------------------------------------------------%%
\section{Introduction}
\label{sec:introduction}

In Ref.~\cite{evans_2003}, we developed a residual Monte Carlo method
that was an application of Halton's Sequential Monte Carlo
method~\cite{halton_1962,halton_1994} to the 1D equilibrium (1T)
thermal radiation diffusion equation.  At that time, Halton's method
was not widely known in computational physics.  While extending our
method to 3D, we have discovered that the Sequential Monte Carlo
method is actually a variant of iterative refinement cast as a
residual method.  Using Monte Carlo to accelerate fixed-point
(Richardson) iteration, our new method surpasses our previous 1D
method and allows for extension to more general solution techniques.

The purpose of this study is to demonstrate an efficient Monte Carlo
solution method for 3D, time-dependent discrete systems.  In this
note, we extend our previous work in the following manner:
\begin{itemize}
\item We develop a rigorous synthetic-acceleration Monte Carlo method
  for solving sparse matrix systems.
\item We apply this solver to the 1T thermal radiation diffusion
  equation in 3D.
\end{itemize}
In \S~\ref{sec:monte-carlo-matrix} we review Monte Carlo methods for
solving matrix systems. In \S~\ref{sec:iter-refin-monte} we discuss
our new synthetic-acceleration scheme and connect with previous work
by Halton~\cite{halton_1994} and others~\cite{evans_2003}.  The 1T
radiation diffusion equation and its discrete form will be derived in
\S~\ref{sec:discr-form-radi}.  We discuss using Synthetic-Accleration
Monte Carlo to solve the discrete radiation diffusion equation in
\S~\ref{sec:solut-radi-diff}.  Results from two 3D test problems are
given in \S~\ref{sec:results}.  We finish with conclusions and ideas
for future work in \S~\ref{sec:conclusions}.
